COSC3500 \\ 2D Orbital Simulation Report

### 2018-10-19 reports/ms1_report.tex
Append everything

@@

\end{document}

>>>>

We failed to find the threshold where MPI overhead gave way to a parallel speedup. Future testing plans may require even higher numbers of bodies.

Testing with higher counts of bodies caused transient out-of-memory issues that persisted even after requests for more memory per node were made. This dramatically reduced the statistical significance of tests with 16384 bodies.

@@

\section*{Appendix}

\includegraphics[width=4.4cm]{4-cpusPerTask-nodes}
\includegraphics[width=4.4cm]{4-cpusPerTask-tasksPerNode}
\includegraphics[width=4.4cm]{4-nodes-tasksPerNode}
\includegraphics[width=4.4cm]{4-cpusPerTask-nodes-elide_8_tpn}
\includegraphics[width=4.4cm]{4-cpusPerTask-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{4-nodes-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{4-cpusPerTask-nodes-just_1_tpn}

\includegraphics[width=4.4cm]{16-cpusPerTask-nodes}
\includegraphics[width=4.4cm]{16-cpusPerTask-tasksPerNode}
\includegraphics[width=4.4cm]{16-nodes-tasksPerNode}
\includegraphics[width=4.4cm]{16-cpusPerTask-nodes-elide_8_tpn}
\includegraphics[width=4.4cm]{16-cpusPerTask-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{16-nodes-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{16-cpusPerTask-nodes-just_1_tpn}

\includegraphics[width=4.4cm]{64-cpusPerTask-nodes}
\includegraphics[width=4.4cm]{64-cpusPerTask-tasksPerNode}
\includegraphics[width=4.4cm]{64-nodes-tasksPerNode}
\includegraphics[width=4.4cm]{64-cpusPerTask-nodes-elide_8_tpn}
\includegraphics[width=4.4cm]{64-cpusPerTask-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{64-nodes-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{64-cpusPerTask-nodes-just_1_tpn}
\includegraphics[width=4.4cm]{256-cpusPerTask-nodes}
\includegraphics[width=4.4cm]{256-cpusPerTask-tasksPerNode}
\includegraphics[width=4.4cm]{256-nodes-tasksPerNode}
\includegraphics[width=4.4cm]{256-cpusPerTask-nodes-elide_8_tpn}
\includegraphics[width=4.4cm]{256-cpusPerTask-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{256-nodes-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{256-cpusPerTask-nodes-just_1_tpn}

\includegraphics[width=4.4cm]{1024-cpusPerTask-nodes}
\includegraphics[width=4.4cm]{1024-cpusPerTask-tasksPerNode}
\includegraphics[width=4.4cm]{1024-nodes-tasksPerNode}
\includegraphics[width=4.4cm]{1024-cpusPerTask-nodes-elide_8_tpn}
\includegraphics[width=4.4cm]{1024-cpusPerTask-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{1024-nodes-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{1024-cpusPerTask-nodes-just_1_tpn}

\includegraphics[width=4.4cm]{4096-cpusPerTask-nodes}
\includegraphics[width=4.4cm]{4096-cpusPerTask-tasksPerNode}
\includegraphics[width=4.4cm]{4096-nodes-tasksPerNode}
\includegraphics[width=4.4cm]{4096-cpusPerTask-nodes-elide_8_tpn}
\includegraphics[width=4.4cm]{4096-cpusPerTask-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{4096-nodes-tasksPerNode-elide_8_tpn}
\includegraphics[width=4.4cm]{4096-cpusPerTask-nodes-just_1_tpn}
\end{document}
